---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# snoop

<!-- badges: start -->
[![R-CMD-check](https://github.com/Reckziegel/snoop/workflows/R-CMD-check/badge.svg)](https://github.com/Reckziegel/snoop/actions)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

> A package for backtesting and data`snoop`ing.

## Installation

You can install the development version of snoop from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("Reckziegel/snoop")
```

## Workflow

`snoop` aims to automate routines for portfolio construction purposes inside the `tiyverse`.

The current workflow is the following:

1. Build a rolling `tibble` with `construct_rolling_infrastructure()`
2. Chose a rebalance periodicity with `construct_rebalance_infrastructure()`
3. Rebalance with `rebalance_portfolio()`
4. Compute the main statistics with `extract_statistics()`

## Toy Example

```{r}
library(snoop)

# Step 0: Get the data
stocks <- tibble::tibble(
 time = as.Date('2009-01-01') + 0:99,
 X    = stats::rnorm(100, 0, 1),
 Y    = stats::rnorm(100, 0, 2),
 Z    = stats::rnorm(100, 0, 4)
)

# Step 1: Rolling Infraestructure
roll <- construct_rolling_infrastructure(stocks, .initial = 50)
roll

# Step 2: Rebalance Infraestructure
rebal <- construct_rebalance_infrastructure(roll, .by = "week")
rebal # information is under the hood

# Step 3: Rebalance Portfolio
mu_sigma <- function(.data) {
  # Mean Variance Strategy
  list(mu = colMeans(.data), sigma = stats::cov(.data)) 
}

# Step 4: Compute the main statistics
optimal <- rebalance_portfolio(rebal, mu_sigma, .strategy = "mean_variance")
optimal

# Step 4: Compute Statistics
metrics <- extract_statistics(optimal)
metrics
```
